A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-12 doc/draft-01-stokes/04numerical.tex
minor edits

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
\caption{Sample discretization of an annulus 1<r<1.7, where the inner
circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
is discretized using $10$ panels.}
\label{fig:panels}
\end{figure}
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $j$
by $A(j)$. On a closed curve,
$A(j)$ contains two integers.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_barbell_001_bdry}
    \caption{A barbell-shaped domain.}
    \label{subfig:barbell_bdry}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_bdry}
    \caption{A domain with several inclusions.}
    \label{subfig:many_inclusions_bdry}
  \end{subfigure}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_west}
    \caption{Smallest singular value of the BIE operator
      for the computed roots (original intervals)
      along with an estimate of the error in the root (dotted).}
    \label{subfig:many_inclusions_sings_west}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_ref}
    \caption{Smallest singular value of the BIE operator
      for the computed roots on the original intervals (\textbullet)
      and the values obtained on the refined interval ($\times$).}
    \label{subfig:many_inclusions_sings_ref}
  \end{subfigure}
  \caption{Further diagnostics for the eigenvalues of a domain
    with several inclusions.}
  \label{fig:many_inclusions_diagnostics_2}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{media/annulus_discretization.pdf}
\caption{Sample discretization of an annulus, where the inner
circle, $r=1$ is discretized using $6$ panels and the outer circle $r=1.7$
is discretized using $10$ panels.}
\label{fig:panels}
\end{figure}
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $j$
by $A(j)$. On a closed curve,
$A(j)$ contains two integers.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_barbell_001_bdry}
    \caption{A barbell-shaped domain.}
    \label{subfig:barbell_bdry}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_bdry}
    \caption{A domain with several inclusions.}
    \label{subfig:many_inclusions_bdry}
  \end{subfigure}
  \caption{Computational domains.}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_west}
    \caption{Smallest singular value of the BIE operator
      for the computed roots on the original intervals (\textbullet)
      and an estimate of the error (dotted).}
    \label{subfig:many_inclusions_sings_west}
  \end{subfigure}
  ~
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{fig/ex_many_holes_004_sings_plot_ref}
    \caption{Smallest singular value of the BIE operator
      for the computed roots on the original intervals (\textbullet)
      and the values obtained on the refined interval ($\times$).}
    \label{subfig:many_inclusions_sings_ref}
  \end{subfigure}
  \caption{Further diagnostics for the eigenvalues of a domain
    with several inclusions.}
  \label{fig:many_inclusions_diagnostics_2}
\end{figure}
